### 2021-02-24 evaluation.tex
Improve some wording
Add and extend some todos
some initial comments to experiments

@@

The scripts that were used to generate the training data and to train and evaluate the recommender
are available at the following URL:
\url{https://github.com/filipbartek/vampire-ml/tree/6907ee35}
\todo{FB: Tag the version and link to the tag.}
\todo{FB: Add some wrapper scripts and readme for ease of use.}

@@

All the experiments were run on a computer with
the CPU Intel Xeon Gold 6140 (72 cores @ \SI{2.30}{GHz}),
\SI{383}{GiB} RAM,
the OS Ubuntu 20.04 and
the Linux kernel 5.4.0-40-generic.

@@

The empirical evaluation was performed using a modified version of the \gls{atp} \Vampire{} 4.3.0 \cite{10.1007/978-3-642-39799-8_1}.
The prover was used to generate the training data and to evaluate the trained precedence recommender.
To generate the training data,
\Vampire{} was modified to output \gls{cnf} representations of the problems
and annotated problem signatures in a machine-readable format.
%in \gls{json} format and annotated problem signatures in \gls{csv} format.\todo{MS: Mentioning JSON or CSV seems to be too low level. ``programmer documatation'' material.}
For the evaluation of the precedences generated by the recommender,
\Vampire{} was modified to allow the user to supply explicit predicate and function symbol precedences for the proof search
(normally, the user only picks a precedence generation heuristic).
The modified version of \Vampire{} is available at the following URL:
\url{https://github.com/filipbartek/vampire/tree/3bbfa9e6}

\todo[inline,author=MS]{Literal comparison mode is not a standard thing. Mentioning the option name is again too low level. Explaining the effect (point two) is appropriate, although a bit too vague. To kdyztak opravim ja. 
Popsat presne setup je dulezite, kvuli reprodukovatelnosti, ale ne nutne primo v clanku (budem nejspis stejne dodavat odkaz na nejake reproducibility repo).
Ted zminit AVATAR je nevhodne, pokud nevysvetlis, co to aspon ramcove je. A pokud to budes vysvetlovat, je otazka, proc tim ztracet misto, kdyz to neni bezprostredne relevantni pro dalsi vysvetlovani.}

\Vampire{} was run with a time limit of 10 seconds.
To increase the potential impact of predicate precedences,
we used a simple \gls{tkbo} \cite{Ludwig2007,Kovacs2011}
that compares atoms according to the predicate precedence first,
using the regular \gls{kbo} to break ties between atoms
and to compare terms.
\todo[inline,author=FB]{Describe the detailed configuration in an appendix and reference the appendix here.}

@@

\subsubsection{Sampling}

@@

To ensure the efficiency of the sampling, the process is interpreted as an instance of Bernoulli multi-armed bandit problem,
\todo{Cite? MS: kdyz bude dobra citace, sem by se urcite sikla:) Pri nejhorsim Sutton \& Barto to jisti.}
with the reward of a trial being 1 in case an example is produced, and 0 otherwise.
Adaptive sampling balances
exploring problems that have been tried relatively scarcely and
exploiting problems that have yielded examples relatively often.
For each problem $P \in \ProblemsTptp$,
the generator keeps track of the number of times the problem has been tried $n_P$
and the number of examples generated from that problem $s_P$.
The ratio of $s_P$ to $n_P$ corresponds to the average reward of problem $P$ observed so far.
The problems are sampled using the allocation strategy \acrshort{ucb1} \cite{Auer2002} with a parallelizing relaxation.
In each iteration, the generator samples the problem $P$ that maximizes
$\frac{s_P}{n_P} + \sqrt{\frac{2 \ln n}{n_P}}$,
\todo{FB: Shrink into text to save space.}
where $n = \sum_{P \in \ProblemsTptp} n_P$ is the total number of tries on all problems.
The parallelizing relaxation means that the $s_P$ values are only updated once in \num{1000} iterations,
allowing up to \num{2000} parallel solver executions.
\todo{Explain in detail?}

The sampling runs until a target number of examples is generated---\num{1000000} predicate precedence examples and \num{800000} function precedence examples.
% sftp://cluster.ciirc.cvut.cz/home/bartefil/git/vampire-ml/out/20210108-generate-predicate/questions_generated
For example, while generating \num{1000000} examples for the predicate precedence dataset,
the least explored problem was tried 19 times, and the most exploited problem was tried 504 times.
\num{5349} out of the \num{17053} problems yielded at least one example.

\subsubsection{Split}

>>>>

\todo[inline]{FB: Scan through this section and make sure we use "we" form and past tense consistently.}

@@

The scripts that were used to generate the training data and to train and evaluate the recommender
are available at the following URL:
\url{https://github.com/filipbartek/vampire-ml/tree/6907ee35}
\todo{FB: Tag the version and link to the tag.}
\todo{FB: Add some wrapper scripts and readme for ease of use.}
\todo{MS: Obycejne schovavan URL do footnote, at tolik netrci!
Taky se da zkratit, napriklad pomoci \url{git.io}.}

@@

All the experiments were run on a computer with
the CPU Intel Xeon Gold 6140 (72 cores @ \SI{2.30}{GHz}),
\SI{383}{GiB} RAM,
the OS Ubuntu 20.04 and
the Linux kernel 5.4.0-40-generic.
\todo{FB: Add version of Python and notable packages, namely DGL and TensorFlow. 
MS: Z tohohle bych vetsinu nebo vsechno prenesl do README na adrese vyse.
Stejne ten paper neobsahuje dost informaci na to, aby si to mohl po nas nekdo naprogramovat a spustit.
Tak uz muze byt uplne jedno, jakou mame verzi Linuxu...}

@@

The empirical evaluation was performed using a modified version of the \gls{atp} \Vampire{} 4.3.0 \cite{10.1007/978-3-642-39799-8_1}.
The prover was used to generate the training data and to evaluate the trained precedence recommender.
To generate the training data,
\Vampire{} was modified to output \gls{cnf} representations of the problems
and annotated problem signatures in a machine-readable format.
%in \gls{json} format and annotated problem signatures in \gls{csv} format.\todo{MS: Mentioning JSON or CSV seems to be too low level. ``programmer documatation'' material.}
For the evaluation of the precedences generated by the recommender,
\Vampire{} was modified to allow the user to supply explicit predicate and function symbol precedences for the proof search
(normally, the user only picks a precedence generation heuristic).
The modified version of \Vampire{} is available at the following URL:
\url{https://github.com/filipbartek/vampire/tree/3bbfa9e6} \todo{MS: nebo jeste lip. Slo by udelat repo, 
ve kterym bude textak, co vsechno vysvetli, vcetne linku na ty dve repa co zminujes tady a vyse.}

\Vampire{} was run with a time limit of 10 seconds.
To increase the potential impact of predicate precedences,
we used a simple \gls{tkbo} \cite{Ludwig2007,Kovacs2011}
that compares atoms according to the predicate precedence first,
using the regular \gls{kbo} to break ties between atoms
and to compare terms (using the \Vampire{} option \texttt{-literal\_comparison\_mode predicate}).\todo{MS: ted s vysvetlenim neni naskodu zminit i option name 
``Vampire'' se tim chlubi, ze to ma naimplementovane a my tim rikame, ze jsme si to neprogramovali sami.}
\todo[inline,author=FB]{Describe the detailed configuration in an appendix and reference the appendix here.}

@@

\subsubsection{Examples generation}

@@

To ensure the efficiency of the sampling, the process is interpreted as an instance of Bernoulli multi-armed bandit problem \cite{Sutton1998},
with the reward of a trial being 1 in case an example is produced, and 0 otherwise.
Adaptive sampling balances
exploring problems that have been tried relatively scarcely and
exploiting problems that have yielded examples relatively often.
For each problem $P \in \ProblemsTptp$,
the generator keeps track of the number of times the problem has been tried $n_P$
and the number of examples generated from that problem $s_P$.
The ratio of $s_P$ to $n_P$ corresponds to the average reward of problem $P$ observed so far.
The problems are sampled using the allocation strategy \acrshort{ucb1} \cite{Auer2002} with a parallelizing relaxation.
In each iteration, the generator samples the problem $P$ that maximizes
$\frac{s_P}{n_P} + \sqrt{\frac{2 \ln n}{n_P}}$,
\todo{FB: Shrink into text to save space.}
where $n = \sum_{P \in \ProblemsTptp} n_P$ is the total number of tries on all problems.
The parallelizing relaxation means that the $s_P$ values are only updated once in \num{1000} iterations,
allowing up to \num{2000} parallel solver executions.
\todo{Explain in detail?}

The sampling runs until a target number of examples is generated---\num{1000000} predicate precedence examples and \num{800000} function precedence examples.
\todo{FB: Prevent confusion of dash for minus.}
% sftp://cluster.ciirc.cvut.cz/home/bartefil/git/vampire-ml/out/20210108-generate-predicate/questions_generated
For example, while generating \num{1000000} examples for the predicate precedence dataset,
the least explored problem was tried 19 times, and the most exploited problem was tried 504 times.
\num{5349} out of the \num{17053} problems yielded at least one example.

\subsubsection{Validation split}
